Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality

### 2015-06-12 content/personal-details-els.tex
Added the CORRECT article class, and set up the template correctly apart from the problem listed below.  Also fixed the details for Rehab in all the personal-details-*.tex
PROBLEMS
- inductive step still overflows both column and page
- abstract or the rest of the frontmatter does not format properly in twocolumn mode

% Personal Details
\begin{frontmatter}
	\title{Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality}
	\runningtitle{CoDeR Model and R4 Algorithm: Continuous Deductive Reasoning over Streamed RDF Data}

	\review{}{}{}

	\author{\fnms{David L.} \snm{Monks}}
	\sep
	\author{\fnms{Rehab} \snm{?}}
	and
	\author{\fnms{Nicholas M.} \snm{Gibbins}}
	\runningauthor{D.L. Monks et al.}
	\address{
	          Department of Electronics and Computer Science,\\
	          Faculty of Physical Sciences and Engineering,\\
	          University of Southampton,\\
	          University Rd., Southampton, SO17 1BJ,\\
	          United Kingdom\\
	          E-mail: \{dm11g08,r???,nmg\}@ecs.soton.ac.uk
	}
	% TODO fix Rehab's details

>>>>

% Personal Details
\begin{frontmatter}
	\title{Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality}

	\author{David L. Monks}
	\ead{dm11g08@ecs.soton.ac.uk}
	\author{Rehab Albeladi}
	\ead{raab1g09@ecs.soton.ac.uk}
	\author{Nicholas M. Gibbins}
	\ead{nmg@ecs.soton.ac.uk}
	% \ead{\{dm11g08,raab1g09,nmg\}@ecs.soton.ac.uk}
	\address{
	          Department of Electronics and Computer Science,\\
	          Faculty of Physical Sciences and Engineering,\\
	          University of Southampton,\\
	          University Rd., Southampton, SO17 1BJ,\\
	          United Kingdom
	}
	% TODO fix Rehab's details
